---
title: "Scraping"
author: "Anton"
date: "6/17/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# To-do

- grab meet name
- grab athlete name
- grab meet date
- grab non-multi-event results


# Libraries
```{r}
library(rvest)
library(stringr)
```

# Fixed inputs for parsing

 regex for each event, assuming there is some form of whitespace preceeding it
 ?<= is a positive look behind. It then looks for 
 the backslashes with s is white space. {0, 1000} between this many spaces
 d(1,2) one or two digits followed by a decimal followed by another two decimals


```{r}
re100 <- "(?<=\\s{0,1000}+)(\\d{1,2}\\.\\d{1,2})"
reLJ <- "(?<=\\s{0,1000}+)(\\d{1}\\.\\d{1,2})"
reSP <- "(?<=\\s{0,1000}+)(\\d{1,2}\\.\\d{1,2}m)"
reHJ <- "(?<=\\s{0,1000}+)(\\d{1}\\.\\d{1,2}m)"
re400 <- "(?<=\\s{0,1000}+)(\\d:){0,1}(\\d{2}\\.\\d{1,2})"
re110H <- "(?<=\\s{0,1000}+)(\\d{2}\\.\\d{1,2})"
reDT <- "(?<=\\s{0,1000}+)(\\d{1,2}\\.\\d{1,2}m)"
rePV <- "(?<=\\s{0,1000}+)(\\d{1}\\.\\d{1,2}m)"
reJT <- "(?<=\\s{0,1000}+)(\\d{1,2}\\.\\d{1,2}m)"
re1500 <- "(?<=\\s{0,1000}+)(\\d:){1}(\\d{2}\\.\\d{1,2})"

eventScoresRe <- c(re100, reLJ, reSP, reHJ, re400, re110H, reDT, rePV, reJT, re1500)
eventNames <- c("100", "LJ", "SP", "HJ", "400", "110H", "DT", "PV", "JT", "1500")
```

# One Athlete Extract
```{r}
#oneAthlete <- read_html("https://www.tfrrs.org/athletes/6972495/Michigan/Ayden_Owens")
oneAthlete <- read_html("https://www.tfrrs.org/athletes/6997786/Georgia/Karel_Tilga")
oneAthlete
```

```{r}
tables <- oneAthlete %>% 
    html_nodes("table")
# for some reason html_nodes doesn't recognize tbody tags

dec <- grep("Dec\\n", tables, perl = TRUE)

decRes <- tables[dec] %>% html_text() # contains all scores related to the decathlon

# str_extract(decRes, "(?s)(?<=100).*") # hard coding that returns everything after the 100
decEventNames <- c("100", "LJ", "SP", "HJ", "400", "110H", "DT", "PV", "JT", "1500")
eventNameRe <- paste0("(?s)(?<=", decEventNames,").*")


dec_scores = vector(mode = "list", length = length(decRes))
for(i in 1:length(eventNameRe)) {
    allTextAfter <- str_extract(decRes, eventNameRe[i])
    dec_scores[[i]] <-
        str_extract(allTextAfter, eventScoresRe[i])
    names(dec_scores)[[i]] <- eventNames[i]
}
dec_scores
```

