---
title: "Heptathlon"
author: "VNV Rao"
date: "7/11/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE, message=FALSE)
library(tidyverse)
library(dplyr)
library(readr)
library(tidyLPA)
library(ggplot2)
library(plotly)
```

# Purpose

This document contains the data analysis of Heptathlon World Championships results. The purpose of this analysis is to conduct a latent profile analysis on event scores from the last five World Championships. 



# DATA 

```{r}
hep=read_csv("heptathlonworldchampionships.csv")
names(hep)[1]="Competition"
names(hep)
hepnomiss=na.omit(hep)
summary(hep)
```


# Correlation Matrix

```{r}
round(cor(hep[,4:10], use="pairwise.complete.obs"),3)
```

We see from the correlation matrix that the HJ is strongly correllated with the LJ. The LJ is strongly correlated with the running events. The shorter running events are strongly correlated with eachother and the LJ. The 800m is strongly correlated with the LJ. The throwing events are strongly correlated with eachother and the HJ.

^ compare this to that 2011 SEM

# LPA

```{r}
hepnomiss[,4:10] %>% 
  estimate_profiles(
    2:4, 
    variances = c("equal","varying","equal","varying"), 
    covariances = c("zero","zero","equal","varying")
  )
```

Not really sure how to pick a model, or how the variances covariances stuff works across profiles, but I guess model type 3 with 3 classes is best? lowest AIC, one of the lowest BICs, one of the highest entropy's, and BLRT_p is .62 to add a 4th class. 


```{r}
#final model
lpa3 <- hepnomiss[,4:10] %>% 
  estimate_profiles(
    3,
    variances = "equal", 
    covariances = "equal"
  ) 

hepnomiss[11:14] <- tidyLPA::get_data(lpa3)[10:13]
names(hepnomiss)[14]="profile"
hepnomiss$profile <- factor(hepnomiss$profile, labels=c("runner","thrower","allrounder"))
```


```{r}
get_estimates(lpa3) %>% 
  filter(Category=="Means") %>% 
  group_by(Class) %>% 
  summarise(
    AveTot=sum(Estimate)
  )
```
Looks like Class 1 is, on average, best. 


```{r}
plot_profiles(lpa3)
```
Looks like: 
- Profile 1 (like KJT) is runners who also are good jumpers and are horrible throwers. 
- Profile 2 (like Nafi) is throwers, particularly good at shotput, who really can't run distance, but are pretty decent everywhere else.
- Profile 3 seems to be allrounders, who are pretty good at all events. 

```{r}
hepnomiss %>% filter(profile=="runner")
hepnomiss %>% filter(profile=="thrower")
hepnomiss %>% filter(profile=="allrounder")
```
## correlation matrix of events, just for class 1, the runners
```{r}
round(cor((hepnomiss %>% filter(profile=="runner"))[,4:10], use="pairwise.complete.obs"),3)
```
## correlation matrix of events, just for class 2, the throwers
```{r}
round(cor((hepnomiss %>% filter(profile=="thrower"))[,4:10], use="pairwise.complete.obs"),3)
```

## correlation matrix of events, just for class 3, the all-rounders
```{r}
round(cor((hepnomiss %>% filter(profile=="allrounder"))[,4:10], use="pairwise.complete.obs"),3)
```

## parallel coordinates plot
```{r}
hep2 <- hepnomiss %>% rowwise() %>% mutate(total.score = sum(HJ+LJ+SP+JT+mh100+m200+m800))

fig <- hep2 %>% filter(profile=="runner") %>% 
  
  plot_ly(type = 'parcoords',
          line = list(color = ~as.numeric(profile), colorscale=list(c(0,'red'),c(0.5,'green'),c(1,'blue'))),
          dimensions = list(
              list(range = c(800,1200),
                   label = 'mh100', values = ~mh100),
              list(range = c(750,1200),
                   label = 'HJ', values = ~HJ),
              list(range = c(550,1000),
                   label = 'SP', values = ~SP),
              list(range = c(725,1125),
                   label = 'm200', values = ~m200),
              list(range = c(650,1125),
                   label = 'LJ', values = ~LJ),
              list(range = c(500,1050),
                   label = 'JT', values = ~JT),
              list(range = c(625,1050),
                   label = 'm800', values = ~m800),
              list(range = c(5250,7250),
                   label = 'total', values = ~total.score)
            )
  )


fig

```





# Clustering

I gotta figure out how to do the LPA. In the meantime, k-means: 

```{r}
wss={}
for (i in 2:7){
wss[i-1]=kmeans(hepnomiss[,4:10],centers=i)$tot.withinss
}
plot(wss)
```
Ummm, so, 3?

```{r}
k3=kmeans(hepnomiss[,4:10],centers=3)
k3$centers
k3$size
apply(k3$centers,1,sum)
```

In k3, cluster 1 is KJT, Cluster 2 is Nafi, Cluster 3 is like people who aren't so good.

```{r}
hepnomiss[which(k3$cluster==2),]
```


```{r}
pca=princomp(hepnomiss[,4:10])
summary(pca)
```

